イーサリアム: 安全な分散型汎用トランザクション台帳\\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-07-19 Paper.tex
[WIP] error:Unicode-character

% We have introduced, discussed and formally defined the protocol of Ethereum. Through this protocol the reader may implement a node on the Ethereum network and join others in a decentralised secure social operating system. Contracts may be authored in order to algorithmically specify and autonomously enforce rules of interaction.
我々は、イーサリアムのプロトコルを紹介し、議論し、正式に定義した。このプロトコルにより、読者はイーサリアムネットワーク上のノードを実装し、分散型の安全な社会的オペレーティングシステムに他の人と参加することができます。

契約は、相互作用のルールをアルゴリズムで指定し、自律的に強制するために作成されるかもしれません

@@

Many thanks to Aeron Buchanan for authoring the \textit{Homestead} revisions, Christoph Jentzsch for authoring the Ethash algorithm and Yoichi Hirai for doing most of the EIP-150 changes. Important maintenance, useful corrections and suggestions were provided by a number of others from the Ethereum DEV organisation and Ethereum community at large including Gustav Simonsson, Pawe\l{} Bylica, Jutta Steiner, Nick Savers, Viktor Tr\'{o}n, Marko Simovic, Giacomo Tazzari and, of course, Vitalik Buterin.

>>>>

We have introduced, discussed and formally defined the protocol of Ethereum. Through this protocol the reader may implement a node on the Ethereum network and join others in a decentralised secure social operating system. Contracts may be authored in order to algorithmically specify and autonomously enforce rules of interaction.

@@

% Many thanks to Aeron Buchanan for authoring the \textit{Homestead} revisions, Christoph Jentzsch for authoring the Ethash algorithm and Yoichi Hirai for doing most of the EIP-150 changes. Important maintenance, useful corrections and suggestions were provided by a number of others from the Ethereum DEV organisation and Ethereum community at large including Gustav Simonsson, Pawe\l{} Bylica, Jutta Steiner, Nick Savers, Viktor Tr\'{o}n, Marko Simovic, Giacomo Tazzari and, of course, Vitalik Buterin.

Homesteadのリビジョンを作成したAeron Buchanan、Ethashのアルゴリズムを作成したChristoph Jentzsch、EIP-150のほとんどの変更を行ったYoichi Hiraiに感謝を表します。
EIP-150の変更のほとんどを行ったYoichi Hiraiです。Gustav Simonsson、Pawe l Bylica、Jutta Steiner、Nick Savers、Viktor Tr´on、Marko Simovic、Giacomo Tazzari、そしてもちろんVitalik Buterinを含むEthereum DEVの組織やEthereumコミュニティ全体から重要なメンテナンス、役に立つ修正、提案が多数提供されました。
